Manual classification of tumor cells

### 2024-05-03 analyses/ewings-cell-type/01-marker-gene-tumor-classification.Rmd
Apply suggestions from code review
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>

```{r}
ggplot(umap_df, aes(x = gene_expression, fill = gene_symbol)) +
  geom_density() +
  theme_bw() +
  facet_wrap(vars(gene_symbol))
```

@@

```{r}
# get the z-scores for all genes, transforming across each column that contains expression for a given gene 
transformed_exp_df <- umap_df |> 
  dplyr::select(barcodes, gene_symbol, gene_expression) |> 
  tidyr::pivot_wider(
    names_from = "gene_symbol",
    values_from = "gene_expression") |> 
  dplyr::mutate(across(!barcodes, ~ scale(.x))) |> 
  tidyr::pivot_longer(
    cols = - barcodes,
    names_to = "gene_symbol",
    values_to = "transformed_gene_expression"
  )

# add the transformed gene expression back to the main df used for plotting
umap_df <- umap_df |> 
  dplyr::left_join(transformed_exp_df, by = c("barcodes", "gene_symbol"))
```

@@

```{r}
ggplot(umap_df, aes(x = transformed_gene_expression, fill = gene_symbol)) +
  geom_density() +
  theme_bw() +
  facet_wrap(vars(gene_symbol))
```

>>>>

```{r}
ggplot(umap_df, aes(x = gene_expression, fill = gene_symbol)) +
  geom_density() +
  theme_bw() +
  facet_wrap(vars(gene_symbol)) +
  theme(legend.position = "none")
```

@@

umap_df <- umap_df |> 
  dplyr::group_by(gene_symbol) |>
  dplyr::mutate(transformed_gene_expression = scale(gene_expression)[, 1] |>
  dplyr::ungroup()

@@

```{r}
ggplot(umap_df, aes(x = transformed_gene_expression, fill = gene_symbol)) +
  geom_density() +
  theme_bw() +
  facet_wrap(vars(gene_symbol)) +
  theme(legend.position = "none")
```
